% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  11pt,
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{5}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{setspace}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother





\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 
\usepackage[]{biblatex}
\addbibresource{references.bib}


\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  breaklinks=true,
  pdfborder={0 0 0}
}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={William's Update},
  pdfauthor={William Clinton Co},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}


\title{William's Update}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Remittances}
\author{William Clinton Co}
\date{July 29, 2025}
\begin{document}
\maketitle
\begin{abstract}
This paper examines the current environment of remittance measurement,
identifying key literature and data sources while also addressing topics
discussed during William and Michael's meeting on July 24, 2025.
\end{abstract}

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}

\setstretch{1}
\section{Introduction}\label{introduction}

Overall, there are now improved methods for measuring remittances
compared to older approaches such as population inference. However,
obtaining accurate data on remittances remains a significant challenge.
To better understand how remittances are measured, a good starting point
is \hyperref[high-priority]{High Priority} which is from the World Bank
Group. Another useful resource is
\hyperref[medium-high-priority]{Medium-High Priority}, provided by the
United Nations Capital Development Fund. The main challenges in
remittance measurement include defining what constitutes a remittance
and distinguishing between different measurement approaches, such as
macro-level and micro-level methods. Although measurement techniques
have become more accurate, considerable errors and uncertainties
persist. For further discussion on measurement reliability, see
\href{https://drive.google.com/file/d/1pAtaJZZPiYqQxYHhQaiGtDIG2D1GC0vw/view?usp=sharing}{Arcangelo
et al., 2023}.

\section{Wise (TransferWise) Business
Model}\label{wise-transferwise-business-model}

Wise is a fintech company that facilitates \textbf{low-cost,
international money transfers}. It operates on a unique peer-to-peer
model.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Core Business Model}\label{core-business-model}

\subsubsection{1. Peer-to-Peer (P2P) Currency
Matching}\label{peer-to-peer-p2p-currency-matching}

Wise avoids moving money across borders by matching users sending in
opposite directions: - E.g., If someone sends CAD to the UK and another
sends GBP to Canada, Wise matches them. - Money stays within local
banking systems, reducing fees and increasing speed.

\subsubsection{2. Revenue from Transfer
Fees}\label{revenue-from-transfer-fees}

Wise charges: - \textbf{Fixed fee} per transaction. - \textbf{Variable
fee} (percentage of the amount sent).

\emph{Example:} A \$1,000 USD transfer to the UK might cost only \$5--7,
compared to \$40+ via a bank.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Dataset on remitances}\label{dataset-on-remitances}

\subsection{Problem (William's Notes) Challenges and Methods in
Measuring Remittance
Transactions}\label{problem-williams-notes-challenges-and-methods-in-measuring-remittance-transactions}

\subsubsection{Low Quality of Data}\label{low-quality-of-data}

\begin{itemize}
\tightlist
\item
  Statistical remittance data are often unreliable or incomplete.
\end{itemize}

\subsubsection{Nature of Remittances}\label{nature-of-remittances}

\begin{itemize}
\tightlist
\item
  \textbf{Heterogeneous}: Numerous small transactions carried out by
  individuals.
\item
  \textbf{Multiple Channels}:

  \begin{itemize}
  \tightlist
  \item
    \textbf{Formal}: e.g., electronic wire transfers.
  \item
    \textbf{Informal}: e.g., hand-carried cash or goods across borders.
  \end{itemize}
\end{itemize}

\subsubsection{Detection and Reporting
Issues}\label{detection-and-reporting-issues}

\begin{itemize}
\tightlist
\item
  \textbf{Small transaction sizes} often evade standard data collection
  systems.
\item
  \textbf{Informal transactions} are typically underreported or excluded
  from balance of payments (BoP) data.
\end{itemize}

\subsection{Measurement Approaches}\label{measurement-approaches}

\subsubsection{Direct Measurement}\label{direct-measurement}

\begin{itemize}
\tightlist
\item
  Includes \textbf{transaction reporting} and \textbf{surveys}.
\item
  Considered ideal when feasible.
\end{itemize}

\subsubsection{Combined Methods}\label{combined-methods}

\begin{itemize}
\tightlist
\item
  Some countries use a \textbf{hybrid approach}:

  \begin{itemize}
  \tightlist
  \item
    Combine \textbf{direct measurement} with \textbf{estimates} where
    data are lacking.
  \end{itemize}
\end{itemize}

\subsubsection{Model-Based Approaches}\label{model-based-approaches}

\begin{itemize}
\tightlist
\item
  Models are used to:

  \begin{itemize}
  \tightlist
  \item
    \textbf{Fill data gaps}.
  \item
    \textbf{Estimate global totals}.
  \end{itemize}
\item
  The \textbf{accuracy} of these models depends on the
  \textbf{reliability of input data}.
\end{itemize}

\subsubsection{Assumptions and
Limitations}\label{assumptions-and-limitations}

\begin{itemize}
\tightlist
\item
  \textbf{Indirect data} require \textbf{assumptions} to convert into
  remittance figures.
\item
  Assumptions must be \textbf{plausible}, but are often
  \textbf{untestable or unverifiable in practice}.
\end{itemize}

\subsection{Observed Datasets}\label{observed-datasets}

\begin{itemize}
\tightlist
\item
  \href{https://sdgstoday.org/dataset/remittances?}{SDGs Today
  Remittance}
\item
  \href{https://databank.worldbank.org/metadataglossary/world-development-indicators/series/BM.TRF.PWKR.CD.DT?}{World
  Bank Remittance}
\item
  \href{https://www.dropbox.com/home/remittance}{Dropbox Remittance
  Folder}
\end{itemize}

\subsection{Literature}\label{literature}

\subsubsection{Takeaway}\label{takeaway}

\paragraph{Summary: Challenges and Improvements in Remittance Data
Collection}\label{summary-challenges-and-improvements-in-remittance-data-collection}

\subparagraph{Key Challenges}\label{key-challenges}

\begin{itemize}
\tightlist
\item
  \textbf{Poor data quality}: Despite increased interest, statistics on
  remittances are still inconsistent and incomplete.
\item
  \textbf{Global discrepancies}: In 2023, reported outward flows were
  only two-thirds of reported inward flows, highlighting growing
  asymmetries.
\item
  \textbf{Informal channels}: A significant share of remittances is sent
  through informal means (e.g., hand-carried cash), which often goes
  untracked.
\item
  \textbf{Inconsistent methods}: Countries use different concepts,
  definitions, and recording practices, leading to classification
  errors.
\item
  \textbf{Impact of digitalization}: The rise of digital platforms,
  especially post-COVID, has reshaped remittance flows, but existing
  measurement tools lag behind.
\end{itemize}

\subparagraph{Ongoing Initiatives}\label{ongoing-initiatives}

\begin{itemize}
\tightlist
\item
  \textbf{RemitStat (World Bank)}
  \href{https://blogs.worldbank.org/en/peoplemove/improving-data-on-remittances--remitstat}{RemitStat}
  : A global initiative involving 46 countries, Eurostat, and the IMF,
  aiming to improve remittance data.
\item
  \textbf{TT-GA (IMF Task Team on Global Asymmetries)}
  \href{https://www.imf.org/external/pubs/ft/bop/2024/pdf/44/BOPCOM\%2024-08\%20-\%20Report\%20of\%20the\%20Task\%20Team\%20on\%20Global\%20Asymmetries\%20\%20Progress\%20and\%20Work\%20Plan\%20for\%202025.pdf}{Preliminary
  Report} : Established in October 2023 to investigate data gaps, legal
  and methodological barriers, and propose solutions.
\end{itemize}

\subsubsection{High Priority}\label{high-priority}

\paragraph{\texorpdfstring{Understanding what defines a remittance
\href{https://www.worldbank.org/en/publication/wdr2023/brief/module-8-remittances}{World
Development Report 2023 (Module
8)}}{Understanding what defines a remittance World Development Report 2023 (Module 8)}}\label{understanding-what-defines-a-remittance-world-development-report-2023-module-8}

\begin{itemize}
\item
  \href{https://drive.google.com/file/d/1LL87PIen7uBg9XGSSDZkeXzUWA_HbOCt/view?usp=sharing}{Migrant
  remittances: Alternative money transfer channels}
\item
  \href{https://documents1.worldbank.org/curated/en/099714008132436612/pdf/IDU1a9cf73b51fcad1425a1a0dd1cc8f2f3331ce.pdf\#page=19}{Migration
  and Development Brief (June 2024) (see page 19)}
\item
  \href{https://openknowledge.worldbank.org/server/api/core/bitstreams/6d4f883a-f89d-4fc1-8753-47fb683a3f33/content}{World
  Development Report 2023: Migrants, Refugees, and Societies}
\item
  \href{https://remittanceprices.worldbank.org/sites/default/files/rpw_main_report_and_annex_q424_13.pdf}{Remittance
  Prices Worldwide Quarterly Issue (Dec 2024)}
\item
  \href{https://drive.google.com/file/d/1u0iM0rzaXon-ZQFzc-sfElIgMU54tS8d/view?usp=sharing}{What
  Explains Remittance Fees? (Beck et al., 2022)}
\end{itemize}

\paragraph{Macro Level Measurements}\label{macro-level-measurements}

\begin{itemize}
\tightlist
\item
  \href{https://www.imf.org/external/np/sta/bop/2008/rcg/pdf/guide.pdf}{International
  Transactions in Remittances: Guide for Compilers and Users, October
  2009}
\item
  \href{https://openknowledge.worldbank.org/server/api/core/bitstreams/e90c4fd4-2c7d-4d29-9082-2b4f0484fc2b/content}{World
  Bank Measurement of remittances}
\item
  \href{https://www.imf.org/external/pubs/ft/bop/2007/pdf/bpm6.pdf}{Balance
  of Payments and International Investment Position Manual - Sixth
  Edition (BPM6)}
\end{itemize}

\paragraph{Micro Level Measurements}\label{micro-level-measurements}

\begin{itemize}
\tightlist
\item
  Finding measures with the least noise
  \href{https://drive.google.com/file/d/1pAtaJZZPiYqQxYHhQaiGtDIG2D1GC0vw/view?usp=sharing}{Arcangelo
  et al., 2023}
\item
  Guides on survey design
  \href{https://www.demographic-research.org/volumes/vol31/41/31-41.pdf}{Measuring
  remittances through surveys: Methodological and conceptual issues for
  survey designers and data analysts}
\item
  \href{https://drive.google.com/file/d/1qHRsa8y1B27oIXDuT47WWF27yRyu5Pyj/view?usp=sharing}{How
  reliable are survey estimates of remittances? Evidence from a
  cross-reporting survey exercise}
\end{itemize}

\subsubsection{Medium-High Priority}\label{medium-high-priority}

\begin{itemize}
\tightlist
\item
  \href{https://migrantmoney.uncdf.org/wp-content/uploads/2023/02/Migrant-Money-Note-7-FINAL-1.pdf}{United
  Nations Capital Development Fund}

  \begin{itemize}
  \tightlist
  \item
    \href{https://migrantmoney.uncdf.org/wp-content/uploads/2024/03/Survey-Strategy-and-Questionnaire-on-Estimating-Informal-Remittances.pdf}{Survey
    Strategy and Questionnaire (UNCDF)}
  \item
    \href{https://drive.google.com/file/d/1k0uVC2048y44iZSlEIvRWjE2d-l0HbXu/view?usp=sharing}{See
    Chapter 2, page 13 (Brown and Soto, 2015)}
  \end{itemize}
\end{itemize}

\subsubsection{Low Priority}\label{low-priority}

\begin{itemize}
\tightlist
\item
  \href{https://www.graduateinstitute.ch/sites/internet/files/2024-09/ARP-38-Final-Report--2024----Zeyu-Wei.pdf}{Informal
  Remitances Estimation}

  \begin{itemize}
  \tightlist
  \item
    Uncertain quality
  \end{itemize}
\item
  (Yang,2011)
  \href{https://deanyang-econ.github.io/deanyang/files/yang_2011_jep.25.3.pdf}{Migrant
  Remittances}

  \begin{itemize}
  \tightlist
  \item
    High academic standing
  \item
    Outdated
  \end{itemize}
\item
  \href{https://documents1.worldbank.org/curated/en/850091468163748685/pdf/538840PUB0Migr101Official0Use0Only1.pdf}{World
  Bank Working Paper, 2010}

  \begin{itemize}
  \tightlist
  \item
    Outdated
  \end{itemize}
\end{itemize}


\printbibliography



\end{document}
